### 2018-07-31 ms/ms_probaweb.tex
add extension in path; change for png instead of pdf
attempt to convert to ms word

%\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
%A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
%Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
%Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\

%\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
%biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
%Sherbrooke (Québec). J1K 2R1\\
%\textbf{2}: Québec Centre for Biodiversity Science\\
%\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
%\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
%\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
%\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
%\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
%\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
%\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
%\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
%Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
%\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
%Box 352100, Seattle, WA 98195, USA\\
%\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\

@@

%Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
%concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
%approach and performed the analysis; DG, TP and TR wroted the first draft and
%all of the authors edited the manuscript.

%\newpage
\doublespacing

@@

Biogeography has traditionally focused on the spatial distribution and
abundance of species. Both are driven by the way species interact with one
another, but only recently community ecologists realized these interactions 
vary across time and space and need to be documented.
Here, we call for an integrated approach, adopting the view that community
structure is best represented as a network of ecological interactions, and
show how it translates to biogeography questions. We propose that the
ecological niche should encompass the effect of the environment
on species distribution (the Grinnellian dimension of the niche) and on the
ecological interactions among them (the Eltonian dimension). Starting from
this concept, we develop a quantitative theory to explain turnover of
interactions in space and time -- \emph{i.e.} a novel approach to interaction
distribution modeling. We apply this framework to host–parasite interactions
across Europe and find that two aspects of the environment (temperature and
precipitation) exert a strong imprint on species co-occurrence, but not on
species interactions. Even where species co-occur, interaction proves to be
stochastic rather than deterministic, adding to variation in realized network
structure. We also find that a large majority of host-parasite pairs are never
found together, thus precluding any inferences regarding their probability to
interact. This first attempt to explain variation of network structure at
large spatial scales opens new perspectives at the interface of species
distribution modeling and community ecology.

@@

There are multiple causes of spatial turnover of species co-occurrence. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
either because colonization and extinction events \citep{Hanski1999} are
inherently unpredictable or because strong non-linear feedbacks in community
dynamics generate alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Interaction themselves may impact co-distribution, as
hypothesized long ago by \citet{Diamond1975}. Analyses of community turnover
are usually performed with data represented in a table with rows corresponding
to sites (or measurements) and columns to species. Metrics of beta diversity
quantify the variance of this community data \citep{Legendre2005}. Traditional
approaches rely on measures of dissimilarity among communities, such as the
Jaccard or Bray–Curtis indices. More recent approaches decompose total
variation of the community data into species and site contributions to beta
diversity \citep{Legendre2013}, and further partition it into dissimilarity
due to changes in species richness and dissimilarity due to actual species
turnover \citep{Baselga2010}. Even though all of these methods compare whole
lists of species among sites or measurements, they remain fundamentally
"species-based", since they report variation within columns. None of them
explicitly considers variation of associations (i.e., of pairs or higher-order
motifs – \citealt{Stouffer2007}). Some previous studies have considered how
species distribution could be influenced by the joint effects of the abiotic
and biotic environment \citep{Stephens2009, GonzalezSalasar2013, Cazelles2015,
Ovaskainen2017}, here we inverse the problem and describe how the distribution
of biotic interactions is influenced by species distribution and the
environment.

@@

The first term on the right-hand side of the equation is the probability of
observing the two species co-occurring at location $y$. It corresponds to the
Grinnellian dimension of the niche. The second term represents the probability
that an interaction occurs between species $i$ and $j$, given that they are
co-occurring. This predicate can be refined using information on trait
distribution and trait matching rules \citep{Bartomeus2016}. In short, here we
avoid specific references to traits and considered that interactions are
provided in the data. But one could develop the model further to integrated
them, inspired by the framework in \citealt{Gravel2016}. They proposed to
represent the occurence of an interaction between species as a joint
probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
$\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
respectively. Then after, one may also consider how these traits are related
to the environment and co-occur in order to develop a trait-based
representation of the spatial variation of interactions. Above, we referred to
this entity as the "metaweb" and it corresponds to the Eltonian dimension of
the niche. Below, we will see how this formalism can be directly fit to
empirical data, restricting ourselves to occurrences only and refering to the
above citations for trait-matching and trait-environment relationships. But
before turning to an application, we will discuss the interpretation of
different variants of these two terms

@@

The framework we provide complements methods to compute network beta-
diversity presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total
network turnover is partitionned in interaction turnover and species
turnover, which in our approach would correspond to the three terms of Eq. 2,
respectively. One could easily derive the different $\beta$ of
\citealt{Poisot2012} using the fitted probabilities. For instance, for a pair
of species $i$ and $j$ and sites $x$ and $y$, the expectation for the
fraction $a$ for the interactions would be
$P(L_{ijx}|X_{ix},X_{ijx})P(L_{ijx}|X_{ix},X_{ijx})$. The same could be
computed for factions $b$ and $c$, and therefore the expected beta-diversity
for an entire network could easily be recomputed this way. The interesting
feature of the approach we proposed is that the different partitions for
network turnover could be investigated according to different hypotheses (as
performed here), in order to evaluate for instance the role of environmental
heterogneity or species co-distribution on network turnover.

We restricted our analysis to the effect of co-occurrence on ecological
interactions, neglecting the inverse of the problem. We did not investigate in
depth the drivers of co-occurrence and simply took it for granted from the
data. Co-occurrence was indeed different from the expectation of independent
species distributions. It thus begs the question of whether, once
environmental effects on species-specific distribution have been accounted
for, interactions come with significant effects on co-occurrence? We could
rephrase this problem by asking whether the fundamental niche differs from the
realized niche, and how this applies to our framework. For example, we have
considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
which could be expanded as $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. After some
re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}|E_y
)$, could be considered as a species distribution model taking into account
the interaction between these species (in the same spirit as done by
\citealt{GonzalezSalasar2013}). This derivation would however critically
depend on a strong \emph{a priori} expectation of the conditional probability
of observing a species given the distribution of the other species. This
assumption seems reasonable for some situations, such as a parasitoid species
that requires a host to develop. On the other hand, \citet{Cazelles2016b}
found that the strength of this association is often rather weak if not
inexistant (for instance, with the example pair presented in Table 1). The lack
of an association could simply arise when the parasitoid is generalist enough
that it is not constrained to track the distribution of any single/given host
\citep{Cazelles2015}.

The approach we presented could easily be expanded to account for traits, in
order to have a complete and more mechanistic representation of the niche.
Both the Eltonian and Grinelian dimensions of the niche could be represented
as well. As mentioned earlier, \citealt{Gravel2016} proposed to represent the
occurrence of interactions based on some trait-matching rules (given by a
function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$) and the co-
distribution of traits (corresponding to $P(\mathbf{T}_i, \mathbf{T}_j|E)$).
The key  insight from this formalism proposed by \citealt{Gravel2016} is that
trait co-distribution will impact the variation in network structure. As a
result, it was found that network properties often co-vary with functional
structure and functional diversity \citealp{Laigle2018}. The next step in the
development of this framework will be to develop the models for the trait co-
distribution, for instance following \citealt{Ovaskainen2017}. This may
facilitate the accessibility and the applicability of the framework since the
basic unit of analysis is no more the species, but rather a combination of
traits, thereby facilitating the statistical analysis by sharing information
among species.

@@

Ecological networks are known to be extremely sparse, \emph{i.e.} they have
far more absences than presences of interactions. Absences of interactions,
however, can come from different sources. The fact that unequal sampling at
the local scale can affect our understanding of network structure is well
documented \citep{Martinez1999}. In a spatial context, however, some
interactions may be undocumented simply because the species involved have
never been observed to co-occur. Although these cases are reported as a lack
of interactions, in actuality we cannot make any reliable inference from them:
since the species have never been observed together, it remains possible that
they would interact if they did. A fundamentally different category of
absences of interactions are then those reported after multiple observations
of species co-occurence. Thus, to gain confidence that the probability of an
interaction is low, extensive sampling (that is, several records of co-
occurence) is needed. Generally, our confidence that the interaction is indeed
impossible will increase with the number of observations of the species pair.
Seeing that this is essentially a Bernoulli process (the probability that the
species will interact given their presence), the breadth of the confidence
interval is expected to saturate after a fixed number of observations, which
can be set as a threshold above which a species pair has finally been observed
"often enough". For instance, if two species are observed together at $k=10$
locations but they are never found interacting ($n=0$), this means that the
maximum likelihood estimate for the probability of this binomial distribution
is $p=0$. Using the Clopper-Pearson method to compute the 95\% confidence
interval, we find that the real value of the probability of the interaction
occuring is somewhere between 0 and 0.31. This interval is rather large,
indicating that a significant amount of sampling is required to have credible
interaction networks. Fortunately, there are bayesian methods could be used to
complement available information and reduce this uncertainty
\citep{Cirtwill2018}.

@@

\begin{tabular}{llllllll}
\hline
	Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Temp \\ \hline
	1 & A & B & 0 & 0 & 0 & 0 & 20 \\ 
	2 & A & B & 1 & 1 & 1 & 0 & 21 \\ 
	3 & A & B & 1 & 0 & 0 & 0 & 22 \\ 
	4 & A & B & 0 & 0 & 0 & 0 & 23 \\ 
	5 & A & B & 1 & 1 & 1 & 1 & 24 \\ 
	1 & A & C & 0 & 1 & 0 & 0 & 20 \\ 
	2 & A & C & 1 & 0 & 0 & 0 & 21 \\ 
	3 & A & C & 1 & 1 & 1 & 1 & 22 \\ 
	4 & A & C & 0 & 0 & 0 & 0 & 23 \\ 
	5 & A & C & 1 & 0 & 0 & 0 & 24 \\ 
\hline
\end{tabular}
\end{table}
%\end{landscape}

>>>>

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\

\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
Sherbrooke (Québec). J1K 2R1\\
\textbf{2}: Québec Centre for Biodiversity Science\\
\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
Box 352100, Seattle, WA 98195, USA\\
\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\

@@

Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
approach and performed the analysis; DG, TP and TR wroted the first draft and
all of the authors edited the manuscript.

\newpage
\doublespacing

@@

Biogeography has traditionally focused on the spatial distribution and
abundance of species. Both are driven by the way species interact with one
another, but only recently community ecologists realized the need to document
their spatial and temporal variation. Here, we call for an integrated
approach, adopting the view that community structure is best represented as a
network of ecological interactions, and show how it translates to biogeography
questions. We propose that the ecological niche should encompass the effect of
the environment on species distribution (the Grinnellian dimension of the
niche) and on the ecological interactions among them (the Eltonian dimension).
Starting from this concept, we develop a quantitative theory to explain
turnover of interactions in space and time -- \emph{i.e.} a novel approach to
interaction distribution modeling. We apply this framework to host–parasite
interactions across Europe and find that two aspects of the environment
(temperature and precipitation) exert a strong imprint on species co-
occurrence, but not on species interactions. Even where species co-occur,
interaction proves to be stochastic rather than deterministic, adding to
variation in realized network structure. We also find that a large majority of
host-parasite pairs are never found together, thus precluding any inferences
regarding their probability to interact. This first attempt to explain
variation of network structure at large spatial scales opens new perspectives
at the interface of species distribution modeling and community ecology.

@@

There are multiple causes of spatial turnover of species co-occurrence. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
either because colonization and extinction events \citep{Hanski1999} are
inherently unpredictable or because strong non-linear feedbacks in community
dynamics generate alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Interaction themselves may impact co-distribution, as
hypothesized long ago by \citet{Diamond1975}. Analyses of community turnover
are usually performed with data represented in a table with rows corresponding
to sites (or measurements) and columns to species. Metrics of beta diversity
quantify the variance of this community data \citep{Legendre2005}. Traditional
approaches rely on measures of dissimilarity among communities, such as the
Jaccard or Bray–Curtis indices. More recent approaches decompose total
variation of the community data into species and site contributions to beta
diversity \citep{Legendre2013}, and further partition it into dissimilarity
due to changes in species richness and dissimilarity due to actual species
turnover \citep{Baselga2010}. Even though all of these methods compare whole
lists of species among sites or measurements, they remain fundamentally
"species-based", since they report variation within columns. None of them
explicitly considers variation of associations (i.e., of pairs or higher-order
motifs – \citealt{Stouffer2007}). Some previous studies have considered how
species distribution could be influenced by the joint effects of the abiotic
and biotic environment \citep{Stephens2009, GonzalezSalazar2013, Cazelles2015,
Ovaskainen2017}, here we inverse the problem and describe how the distribution
of biotic interactions is influenced by species distribution and the
environment.

@@

The first term on the right-hand side of the equation is the probability of
observing the two species co-occurring at location $y$. It corresponds to the
Grinnellian dimension of the niche. The second term represents the probability
that an interaction occurs between species $i$ and $j$, given that they are
co-occurring. This predicate can be refined using information on trait
distribution and trait matching rules . For brevity, we have here avoided
specific references to traits and considered that the interactions are
provided in the data. But one could develop the model further to integrate
such traits, inspired by the framework developed by Gravel et al. 2016. They
proposed to represent the occurence of an interaction between species as a
joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
$\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
respectively. In order to develop a trait-based representation of the spatial
variation of interactions, one may thereafter consider how these traits are
related to the environment and how they co-occur. Above, we referred to this
entity as the "metaweb" and note that it corresponds to the Eltonian dimension
of the niche. Below, we will see how this formalism can be directly fit to
empirical data, restricting ourselves to occurrences only and refering to the
above citations for trait-matching and trait-environment relationships. But
before turning to an application, we will discuss the interpretation of
different variants of these two terms.

@@

The framework we provide complements methods to compute network beta-diversity
presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total network
turnover is partitioned into interaction turnover and species turnover – which
in our approach would correspond to the three terms of Eq. 2, respectively.
Importantly, one could easily derive the different $\beta$ of
\citealt{Poisot2012} using the fitted probabilities. For instance, for a pair
of species $i$ and $j$ and sites $x$ and $y$, the expectation for the fraction
$a$ for the interactions would be
$P(L_{ijx}|X_{ix},X_{ijx})P(L_{ijx}|X_{ix},X_{ijx})$. The same could be
computed for fractions $b$, and therefore the expected beta-diversity for an
entire network could be recomputed this way. The novel feature of the approach
presented here is then that the different contributions to network turnover
can be attributed to different hypotheses (as performed here), in order to
evaluate for instance the role of environmental heterogeneity or species co-
distribution on network turnover.

We restricted our analysis to the effect of co-occurrence on ecological
interactions, neglecting the inverse of the problem. We did not investigate in
depth the drivers of co-occurrence and simply took it for granted from the
data. Co-occurrence was indeed different from the expectation of independent
species distributions. It thus begs the question of whether, once
environmental effects on species-specific distribution have been accounted
for, interactions come with significant effects on co-occurrence? We could
rephrase this problem by asking whether the fundamental niche differs from the
realized niche, and how this applies to our framework. For example, we have
considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
which could be expanded as $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. After some
re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}|E_y
)$, could be considered as a species distribution model taking into account
the interaction between these species (in the same spirit as done by Gonzalez-
Salazar et al. 2013). This derivation would however critically depend on a
strong \emph{a priori} expectation of the conditional probability of observing
a species given the distribution of the other species. This assumption seems
reasonable for some situations, such as a parasitoid species that requires a
host to develop. On the other hand, \citet{Cazelles2016b} found that the
strength of this association is often rather weak if not inexistant (for
instance, with the example pair presented in Table 1). The lack of an
association could simply arise when the parasitoid is generalist enough that
it is not constrained to track the distribution of any single/given host
\citep{Cazelles2015}.

The approach we presented could easily be expanded to account for traits, in
order to derive a complete and more mechanistic representation of the niche.
In this context, both the Eltonian and Grinnellian dimensions of the niche
could be represented. As mentioned earlier, \citealt{Gravel2016} proposed to
represent the occurrence of interactions based on some trait-matching rules
(given by a function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$)
and the co-distribution of traits (corresponding to $P(\mathbf{T}_i,
\mathbf{T}_j|E)$). The key  insight from the formalism proposed by
\citealt{Gravel2016} is that the co-distribution of traits will impact
variation in network structure. As a result, it was found that network
properties often co-vary with functional structure and functional diversity
\citealp{Laigle2018}. The next step in the development of this framework will
be to develop the models for the co-distribution of traits, for instance
following Ovaskainen et al. 2017. This may facilitate the accessibility and
the applicability of the framework, since the basic unit of analysis is no
longer the species, but rather a combination of traits, thereby facilitating
the statistical analysis by sharing information among species.

@@

Ecological networks are known to be extremely sparse, \emph{i.e.} they have
far more absences than presences of interactions. Absences of interactions,
however, can come from different sources. The fact that unequal sampling at
the local scale can affect our understanding of network structure is well
documented \citep{Martinez1999}. In a spatial context, however, some
interactions may be undocumented simply because the species involved have
never been observed to co-occur. Although these cases are reported as a lack
of interactions, in actuality we cannot make any reliable inference from them:
since the species have never been observed together, it remains possible that
they would interact if they did. A fundamentally different category of
absences of interactions are then those reported after multiple observations
of species co-occurence. Thus, to gain confidence that the probability of an
interaction is low, extensive sampling (that is, several records of co-
occurence) is needed. Generally, our confidence that the interaction is indeed
impossible will increase with the number of observations of the species pair.
Seeing that this is essentially a Bernoulli process (the probability that the
species will interact given their presence), the breadth of the confidence
interval is expected to saturate after a fixed number of observations, which
can be set as a threshold above which a species pair has finally been observed
"often enough". For instance, if two species are observed together at $k=10$
locations but are never found interacting ($n=0$), this means that the maximum
likelihood estimate for the probability of this binomial distribution is
$p=0$. Using the Clopper-Pearson method to compute the 95\% confidence
interval, we find that the real value of the probability of the interaction
occuring is somewhere between 0 and 0.31. This interval is rather large,
indicating that a significant amount of sampling is required to have credible
interaction networks. Fortunately, there are Bayesian methods which could be
used to complement available information and reduce this uncertainty
\citep{Cirtwill2018}.

@@

\begin{tabular}{llllllll}
\hline
Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
Kühkopf 		& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 1 &  8.25 \\
Kühkopf 		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  8.25 \\
Ötztal 			& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
Ötztal 			& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
Kilpisjärvi		& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
Kilpisjärvi		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
Wüstensachsen	& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 0 &  5.58 \\
Wüstensachsen	& Phyllocolpa leucapsis & Chrysocharis elongata & 1 & 1 & 1 & 1 &  5.58 \\
Steinamoen      & Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\ 
\hline
\end{tabular}
\end{table}
%\end{landscape}
